Differentially Private Bayesian Inference

### 2018-04-03 main.tex
update

To proof this, we discuss some cases:
\begin{itemize}
	\item $\lambda > 0$
	\begin{itemize}
		\item $u(x,r) > 0$
		\item $u(x,r) < 0$
	\end{itemize}
	\item $\lambda < 0$
	\begin{itemize}
		\item $u(x,r) > 0$
		\item $u(x,r) < 0$
	\end{itemize}
\end{itemize}

@@

% \bibliographystyle{icml2018}
% \bibliography{example_paper}

>>>>

To proof this, we discuss some cases:

Since the sensitivity is always greater than 0, but the utility function and $\lambda$ can be positive or negative. That's what we need to discuss.

\begin{itemize}
	\item $\lambda > 0$
	\begin{itemize}
		\item $u(x,r) > 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.

		\item $u(x,r) < 0$

		This need to be discuss further.

	\end{itemize}
	\item $\lambda < 0$
	\begin{itemize}
		\item $u(x,r) > 0$

		This need to be discuss further.

		\item $u(x,r) < 0$

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds.

	\end{itemize}
\end{itemize}

So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.

@@
